---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BIS620.2022.final


**Name: Jingnan Bai**

**NetID: jb3633**


<!-- badges: start -->
[![R-CMD-check](https://github.com/JingnanBai/BIS.620.2022.final/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JingnanBai/BIS.620.2022.final/actions/workflows/R-CMD-check.yaml)
[![lint-check](https://github.com/JingnanBai/BIS.620.2022.final/actions/workflows/lint.yaml/badge.svg)](https://github.com/JingnanBai/BIS.620.2022.final/actions/workflows/lint.yaml)
[![Codecov test coverage](https://codecov.io/gh/JingnanBai/BIS.620.2022.final/branch/master/graph/badge.svg)](https://app.codecov.io/gh/JingnanBai/BIS.620.2022.final?branch=master)
<!-- badges: end -->

This repository is for the final project for BIS620 - Yale University 2022Fall

This package contains basic data cleaning and visualization functions, including:
- replace "?" "Unknown" etc. to NA in R
- exploring possible missing pattern (missing as pair for example)
- deal with missing data by dropping and filling
- outlier exploration and process
- find extremely imbalanced columns and process
- map mark to the true value (ICD-9, other dataset)

Also, it provides basic function for modeling:
- build with WOE coding
- build models for classification, support cross-validation, calculating the best threshold automatically, and model evaluation.
  - Logistic Regression
  - Random Forest
- SMOTE sampling for imbalanced problem

Please refer to /doc/BIS620_2022_final.html for an example that show how this package could be used for finding possible factors of diabetic patients' readmission and build a predictor to estimate the risk.


## Installation

You can install the development version of BIS620.2022.final from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JingnanBai/BIS.620.2022.final")
```

## Example

This is a basic example for data processing and modeling

```{r example}
library(BIS620.2022.final)
## get data
data("diabetic_data")
```

data cleaning for missing value:
```{r fig.height=8, fig.width=8, out.height="60%", out.width="60%"}
mark_list <- c("?", "unknown", "invalid", "not available", "not mapped",
              "null", "none")
diabetic_data <- replace_missing_dataset(diabetic_data, mark_list = mark_list)
res <- missing_explore(diabetic_data)
# show the missing pattern
plot(res$pattern_plot, oma = c(12, 3, 2, 2))
```

for WOE coding:
```{r}
# WOE transformation
res_woe <- build_woe(diabetic_data, ycol = "readmitted",
                               positive = "YES", is_dropsame = TRUE)
diabetic_data_woe <- res_woe$newdata

# get the mapping information for explanation later.
tab_explain_woe <- get_woe_explain(diabetic_data_woe, diabetic_data)
```

for SMOTE:
```{r}
data <- data.frame(y=rep(as.factor(c('Yes', 'No')), times=c(90, 10)), 
                   x1=rnorm(100), x2=rnorm(100))
summary(data$y)
data_smote <- upsample_smote(data, "y")
summary(data_smote$y)
```





